### 2022-02-24 ANA-TOPQ-2019-17-PAPER-metadata.tex
commented out author list that fixed the conflict

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.5}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
\vspace{0.10em}
A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
Standard Model (SM) Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
Large Hadron Collider that corresponds to an integrated luminosity of 139 fb$^{-1}$.
Two processes are considered:  single top quark FCNC production in association with a Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one of top quarks decays into $Wb$ and the other decays into $qH$ through the FCNC interactions.
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ 
with an additional lepton (e,$\mu$),
as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
A slight excess of data is observed above the expected SM background with a significance of 2.3$\sigma$,
and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9 \times 10^{-4}$ ($5.0^{+2.2}_{-1.4}\times 10^{-4}$) and $7.2\times 10^{-4}$ ($3.6^{+1.7}_{-1.0}\times 10^{-4}$), respectively. 
The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.}%for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
%$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.%}
% Author - this does not work with revtex (add it after \begin{document})
\author{The ATLAS Collaboration}

>>>>

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.5}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
Standard Model (SM) Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
Large Hadron Collider that corresponds to an integrated luminosity of 139 fb$^{-1}$.
Two processes are considered:  single top quark FCNC production in association with a Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one of top quarks decays into $Wb$ and the other decays into $qH$ through the FCNC interactions.
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ 
with an additional lepton (e,$\mu$),
as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
A slight excess of data is observed above the expected SM background with a significance of 2.3$\sigma$,
and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9 \times 10^{-4}$ ($5.0^{+2.2}_{-1.4}\times 10^{-4}$) and $7.2\times 10^{-4}$ ($3.6^{+1.7}_{-1.0}\times 10^{-4}$), respectively. 
The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.}%for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
%$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.%}
% Author - this does not work with revtex (add it after \begin{document})
%\author{The ATLAS Collaboration}
